Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-29 paper.tex
Fixup affils
Closes #91

%%% Use the \authfn to add symbols for additional footnotes, if any. 
% 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
% First author
\author[1,\authfn{1}]{Eric Czech}
\author[2,\authfn{1}]{Tim Millar}
\author[3,\authfn{1}]{Tom White}

% Middle
\author[4]{Ben Jeffery}
\author[5]{Alistair Miles}
\author[6]{Sam Tallman}
\author[1]{Rafal Wojdyla}
\author[7]{Shadi Zabad}

% Senior 
\author[8,\authfn{2}]{Jeff Hammerbacher}
\author[4,\authfn{2},\authfn{3}]{Jerome Kelleher}

\affil[1]{Related Sciences}
\affil[2]{Tim's Institute}
\affil[3]{Tom's Institute}
\affil[4]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[5]{Wellcome Sanger Institute}
\affil[6]{Genomics England}
\affil[7]{School of Computer Science, McGill University, Montreal, QC, Canada}
\affil[8]{Jeff's Institute}

>>>>

%%% Use the \authfn to add symbols for additional footnotes, if any. 
% 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
% First author
\author[1,\authfn{1}]{Eric Czech} % https://orcid.org/0000-0002-4254-4255
\author[2,3\authfn{1}]{Timothy R. Millar}
\author[4,\authfn{1}]{Tom White}

% Middle
\author[5]{Ben Jeffery}
\author[6]{Alistair Miles}
\author[7]{Sam Tallman}
\author[1]{Rafal Wojdyla}
\author[8]{Shadi Zabad}

% Senior 
\author[1,\authfn{2}]{Jeff Hammerbacher}
\author[5,\authfn{2},\authfn{3}]{Jerome Kelleher}

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Tom's Institute}
\affil[5]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[6]{Wellcome Sanger Institute}
\affil[7]{Genomics England}
\affil[8]{School of Computer Science, McGill University, Montreal, QC, Canada}
